Title here

### 2024-04-24 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.Rmd
submission weiter

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 8, fig.height = 4, cache = TRUE)
```

@@

In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @ junker2021]. Previous research often relied on self-report questionnaires [@chaplain2008; @liu2020], which may be prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy]. To overcome these limitations, ambulatory assessment methods are recommended [@trull2013ambulatory; @wettstein2020ambulatory], such as measuring physiological parameters like heart rate (HR), offering objective insights into teachers’ stress levels without disrupting their teaching [@donker2018; @runge2020].

@@

@@

The sample consisted of $N$ = 84 pre- and in-service teachers from Germany, who were recruited via personal contact, email lists, and flyers. The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n$ = 81 ($n$ = 52 women, $n$ = 29 men). Participants had a mean age of 30.95 years ($SD$ = 10.90; range: 19-60) and an average teaching experience of 5.64 years ($SD$ = 9.46; range: 0-37).

@@

```{=latex}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Timeline_ProVision_vertical.png}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
\end{figure}
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 8, fig.height = 4, cache = TRUE)

# load packages

library(needs)

needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse,
      ggplot2,
      lavaan,
      lm.beta,
      stargazer)
```

@@

In education, there’s interest in identifying reliable indicators for teacher stress and burnout [@fisher2011; @junker2021]. Previous research often relied on self-report questionnaires [@chaplain2008; @liu2020], which may be prone to biases like social desirability [@razavi2001self] or recall errors [@van2016accuracy]. To overcome these limitations, ambulatory assessment methods are recommended [@trull2013ambulatory; @wettstein2020ambulatory], such as measuring physiological parameters like heart rate (HR), offering objective insights into teachers’ stress levels without disrupting their teaching [@donker2018; @runge2020].

@@

```{r read the data}

# disruption & confidence rating

df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") %>% 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) %>% # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not ask for event
         "confidence_factor",
         "event"
         ) %>% 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

# demographic data

df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>% # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female") # 1 = male; 2 = female
                            ),
            age = LI03_01, 
            teaching_experience = LI04_01)

N_prewrangling <- as.numeric(nrow(df_demo))

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") %>% 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

# heart rate data

data_path <- "./data/heart_rate_data"

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = .$Time - min(.$Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) %>%
    # filter(time <= 600) %>% # filter for 10min intervals
    filter(time <= 7200) %>% # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) %>%
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")

main <- 
  main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  dplyr::summarise(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  filter(!(time_span == "teaching" & time > 600)) %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

N_postwrangling <- as.numeric(length(unique(main$ID)))

stargazer

```

@@

The sample consisted of $N$ = `r N_prewrangling` pre- and in-service teachers from Germany, who were recruited via personal contact, email lists, and flyers. The data of three participants was lost due to failed data transmission, yielding an analysis sample of $n$ = `N_postwrangling` ($n$ = 52 women, $n$ = 29 men). Participants had a mean age of 30.95 years ($SD$ = 10.90; range: 19-60) and an average teaching experience of 5.64 years ($SD$ = 9.46; range: 0-37).

@@

```{=latex}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Timeline.pdf}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
\end{figure}
```

### 2024-04-24 02_paper/02_study/02_fitbit paper/Submission/FitBit_submission.tex
submission weiter

In education, there's interest in identifying reliable indicators for
teacher stress and burnout {[}\citet{fisher2011}; @ junker2021{]}.
Previous research often relied on self-report questionnaires
\citep{chaplain2008, liu2020}, which may be prone to biases like social
desirability \citep{razavi2001self} or recall errors
\citep{van2016accuracy}. To overcome these limitations, ambulatory
assessment methods are recommended
\citep{trull2013ambulatory, wettstein2020ambulatory}, such as measuring
physiological parameters like heart rate (HR), offering objective
insights into teachers' stress levels without disrupting their teaching
\citep{donker2018, runge2020}.

@@

@@

The sample consisted of \(N\) = 84 pre- and in-service teachers from
Germany, who were recruited via personal contact, email lists, and
flyers. The data of three participants was lost due to failed data
transmission, yielding an analysis sample of \(n\) = 81 (\(n\) = 52
women, \(n\) = 29 men). Participants had a mean age of 30.95 years
(\(SD\) = 10.90; range: 19-60) and an average teaching experience of
5.64 years (\(SD\) = 9.46; range: 0-37).

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Timeline_ProVision_vertical.png}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
\end{figure}

>>>>

In education, there's interest in identifying reliable indicators for
teacher stress and burnout \citep{fisher2011, junker2021}. Previous
research often relied on self-report questionnaires
\citep{chaplain2008, liu2020}, which may be prone to biases like social
desirability \citep{razavi2001self} or recall errors
\citep{van2016accuracy}. To overcome these limitations, ambulatory
assessment methods are recommended
\citep{trull2013ambulatory, wettstein2020ambulatory}, such as measuring
physiological parameters like heart rate (HR), offering objective
insights into teachers' stress levels without disrupting their teaching
\citep{donker2018, runge2020}.

@@

\begin{verbatim}
## New names:
## * `` -> `...6`
## * `` -> `...7`
## * `` -> `...8`
## * `` -> `...9`
## * `` -> `...10`
## * `` -> `...11`
\end{verbatim}

\begin{verbatim}
## Warning in left_join(main, df_merge, by = "ID"): Detected an unexpected many-to-many relationship between `x` and `y`.
## i Row 1 of `x` matches multiple rows in `y`.
## i Row 1 of `y` matches multiple rows in `x`.
## i If a many-to-many relationship is expected, set `relationship =
##   "many-to-many"` to silence this warning.
\end{verbatim}

\begin{verbatim}
## function (..., type = "latex", title = "", style = "default", 
##     summary = NULL, out = NULL, out.header = FALSE, column.labels = NULL, 
##     column.separate = NULL, covariate.labels = NULL, dep.var.caption = NULL, 
##     dep.var.labels = NULL, dep.var.labels.include = TRUE, align = FALSE, 
##     coef = NULL, se = NULL, t = NULL, p = NULL, t.auto = TRUE, 
##     p.auto = TRUE, ci = FALSE, ci.custom = NULL, ci.level = 0.95, 
##     ci.separator = NULL, add.lines = NULL, apply.coef = NULL, 
##     apply.se = NULL, apply.t = NULL, apply.p = NULL, apply.ci = NULL, 
##     colnames = NULL, column.sep.width = "5pt", decimal.mark = NULL, 
##     df = TRUE, digit.separate = NULL, digit.separator = NULL, 
##     digits = NULL, digits.extra = NULL, flip = FALSE, float = TRUE, 
##     float.env = "table", font.size = NULL, header = TRUE, initial.zero = NULL, 
##     intercept.bottom = TRUE, intercept.top = FALSE, keep = NULL, 
##     keep.stat = NULL, label = "", model.names = NULL, model.numbers = NULL, 
##     multicolumn = TRUE, no.space = NULL, notes = NULL, notes.align = NULL, 
##     notes.append = TRUE, notes.label = NULL, object.names = FALSE, 
##     omit = NULL, omit.labels = NULL, omit.stat = NULL, omit.summary.stat = NULL, 
##     omit.table.layout = NULL, omit.yes.no = c("Yes", "No"), order = NULL, 
##     ord.intercepts = FALSE, perl = FALSE, report = NULL, rownames = NULL, 
##     rq.se = "nid", selection.equation = FALSE, single.row = FALSE, 
##     star.char = NULL, star.cutoffs = NULL, suppress.errors = FALSE, 
##     table.layout = NULL, table.placement = "!htbp", zero.component = FALSE, 
##     summary.logical = TRUE, summary.stat = NULL, nobs = TRUE, 
##     mean.sd = TRUE, min.max = TRUE, median = FALSE, iqr = FALSE) 
## {
##     save.warn.option <- getOption("warn")
##     options(warn = -1)
##     return(.stargazer.wrap(..., type = type, title = title, style = style, 
##         summary = summary, out = out, out.header = out.header, 
##         column.labels = column.labels, column.separate = column.separate, 
##         covariate.labels = covariate.labels, dep.var.caption = dep.var.caption, 
##         dep.var.labels = dep.var.labels, dep.var.labels.include = dep.var.labels.include, 
##         align = align, coef = coef, se = se, t = t, p = p, t.auto = t.auto, 
##         p.auto = p.auto, ci = ci, ci.custom = ci.custom, ci.level = ci.level, 
##         ci.separator = ci.separator, add.lines = add.lines, apply.coef = apply.coef, 
##         apply.se = apply.se, apply.t = apply.t, apply.p = apply.p, 
##         apply.ci = apply.ci, colnames = colnames, column.sep.width = column.sep.width, 
##         decimal.mark = decimal.mark, df = df, digit.separate = digit.separate, 
##         digit.separator = digit.separator, digits = digits, digits.extra = digits.extra, 
##         flip = flip, float = float, float.env = float.env, font.size = font.size, 
##         header = header, initial.zero = initial.zero, intercept.bottom = intercept.bottom, 
##         intercept.top = intercept.top, keep = keep, keep.stat = keep.stat, 
##         label = label, model.names = model.names, model.numbers = model.numbers, 
##         multicolumn = multicolumn, no.space = no.space, notes = notes, 
##         notes.align = notes.align, notes.append = notes.append, 
##         notes.label = notes.label, object.names = object.names, 
##         omit = omit, omit.labels = omit.labels, omit.stat = omit.stat, 
##         omit.summary.stat = omit.summary.stat, omit.table.layout = omit.table.layout, 
##         omit.yes.no = omit.yes.no, order = order, ord.intercepts = ord.intercepts, 
##         perl = perl, report = report, rownames = rownames, rq.se = rq.se, 
##         selection.equation = selection.equation, single.row = single.row, 
##         star.char = star.char, star.cutoffs = star.cutoffs, suppress.errors = suppress.errors, 
##         table.layout = table.layout, table.placement = table.placement, 
##         zero.component = zero.component, summary.logical = summary.logical, 
##         summary.stat = summary.stat, nobs = nobs, mean.sd = mean.sd, 
##         min.max = min.max, median = median, iqr = iqr, warn = save.warn.option))
## }
## <bytecode: 0x000001fa06756810>
## <environment: namespace:stargazer>
\end{verbatim}

@@

The sample consisted of \(N\) = 84 pre- and in-service teachers from
Germany, who were recruited via personal contact, email lists, and
flyers. The data of three participants was lost due to failed data
transmission, yielding an analysis sample of \(n\) =
\texttt{N\_postwrangling} (\(n\) = 52 women, \(n\) = 29 men).
Participants had a mean age of 30.95 years (\(SD\) = 10.90; range:
19-60) and an average teaching experience of 5.64 years (\(SD\) = 9.46;
range: 0-37).

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{images/Timeline.pdf}
  \caption{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
  \label{Procedure of the two-hour-long study consisting of five phases with five representative 10-minute intervals}
\end{figure}
